Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-17 manuscript/manuscript.Rmd
adds vital rate section to discussion

Using individual and aggregated forms of the same dataset, we were able to directly compare a traditional demographic modeling approach to a population model based on aggregated data. Our quad-based model (QBM) is based on percent cover data and so is in the spirit of density-structured models. In terms of each model's forecasting ability, the IPM outperformed the QBM (Table 1). This is unsurprising since we expected to lose some precision at the aggregated level. However, the underwhelming performance of the QBM could call in the question forecasts that differ from the IPM.

@@

>>>>

### The IPM and QBM produced inconsistent forecasts
Using individual and aggregated forms of the same dataset, we were able to directly compare a traditional demographic modeling approach to a population model based on aggregated data. Our quad-based model (QBM) is based on percent cover data and so is in the spirit of density-structured models. In terms of each model's forecasting ability, the IPM outperformed the QBM (Table 1). This is unsurprising since we expected to lose some precision at the aggregated level. However, the underwhelming performance of the QBM could call in the question forecasts that differ from the IPM.

@@

### The role of vital rate climate dependence
Our intuition was that species with strong climate-dependence on vital rates not well resolved at the aggregate level would result in different forecasts from the two models. For example, survival is very size dependent: smaller individuals have a higher probability of death [@Chu2014]. At the same time, a single small individual contributes relatively little to percent cover estimates at the plot scale. So, if survival of individuals was positively impacted by temperature increases, for example, we would expect to detect this signal in the individual level data but not in the aggregate level data.

### 2015-06-17 manuscript/manuscript.tex
adds vital rate section to discussion

@@

@@

>>>>

\subsubsection{The IPM and QBM produced inconsistent
forecasts}\label{the-ipm-and-qbm-produced-inconsistent-forecasts}

@@

\subsubsection{The role of vital rate climate
dependence}\label{the-role-of-vital-rate-climate-dependence}

Our intuition was that species with strong climate-dependence on vital
rates not well resolved at the aggregate level would result in different
forecasts from the two models. For example, survival is very size
dependent: smaller individuals have a higher probability of death (Chu
and Adler 2014). At the same time, a single small individual contributes
relatively little to percent cover estimates at the plot scale. So, if
survival of individuals was positively impacted by temperature
increases, for example, we would expect to detect this signal in the
individual level data but not in the aggregate level data. However, the
species with recruitment and survival rates most sensitive to climate
factors (\emph{P. secunda}; Fig. 3d) was also the only species for which
the IPM and QBM made consistent forecasts (Fig. 2d).

Individual growth was the most sensitive vital rate to climate factors
for all species (Fig. 3). Individual plant growth, if survival of large
plants is high, likely plays the biggest role in year-to-year percent
cover at the plot level. Therefore, we would naively expect forecasts
from the two models to be consistent. Since this was not the case, and
other vital rates were relatively insensitive to

@@

Chu, C., and P. B. Adler. 2014. When should plant population models
include age structure? Journal of Ecology 102:531--543.
